%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

% Command for printing skill overview bubbles
\newcommand\skills{ 
~
	\smartdiagram[bubble diagram]{
        \textbf{Data}\\\textbf{Engineering},
        \textbf{Full Stack}\\\textbf{~Development~},
        \textbf{Linux}\\\textbf{OS X}\\\textbf{~Windows~},
        \textbf{Writing \&}\\\textbf{Teaching},
        \textbf{GIS \&}\\\textbf{~~Mapping~~},
        \textbf{Statistical}\\\textbf{Analysis},
        \textbf{Mathematical}\\\textbf{~~Modeling~~}
    }
}

% Programming skill bars
\programming{{GIS, Mapping, Remote Sensing / 2.5},
	{Mathematical Modeling / 4}, 
	{Software Development / 6}}

% Projects text
\projects{
\textbf{Languages} - C/C++ $\textbullet$ C\# $\textbullet$ Python $\textbullet$ Ruby $\textbullet$ Javascript $\textbullet$ Scala $\textbullet$ Java $\textbullet$ (No)SQL $\textbullet$ Erlang $\textbullet$ Shell $\textbullet$ etc. \\
\\
        \textbf{Analytics} - Numerical Python $\textbullet$ R $\textbullet$ Matlab/Octave $\textbullet$ D3 $\textbullet$ Graphviz $\textbullet$ etc. \\
        \\
	\textbf{Hardware} - Limited experience in embedded Linux (µCLinux, Blue Cat), Real-Time programming, FPGA programming, and autonomous positioning systems
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{JOHN METTA} % Your name
\cvjobtitle{ Software Architect \\ Mathematical Modeler } % Job
% title/career

\cvlinkedin{/in/johnmetta}
\cvgithub{johnmetta}
\cvnumberphone{(541) 399 1032} % Phone number
\cvsite{johnmetta.com} % Personal website
\cvmail{mail@johnmetta.com} % Email address
\cvnote{\textbf{Pre-marriage Name:} John Pennington}

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar

\section{Summary}
I am an well-rounded full-stack software architect and mathematical modeler. I have developed data analysis systems and user applications in multiple fields from \mbox{remote} sensing to watershed planning to pharmaceutical salesforce assessment.

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
\twentyitem
    	{Apr 2012 –}
	{Aug 2017}
        {Senior Software Developer}
        {\href{http://www.qstream.com/}{Qstream, Inc}}
        {}
        {\begin{itemize}
        \item\textbf{2016-2017:} Integrations Team lead. Provide system-wide data \mbox{integrations}, microservice, and API development and support.
        \item\textbf{2013-2016:} Client Request/Maintenance team lead. Find and troubleshoot system-wide production issues and respond to direct \mbox{programming} needs of clients.
        \item\textbf{2012-2013:} Architect primary data analytics system.
        \end{itemize}
        }

	\twentyitem
    	{Jan 2008 – }
	{Dec 2012}
        {Founder}
        {Hydrasi}
        {}
        {Started a SaaS company providing delivery, visualization, and sharing services for scientific and environmental data. Company found some initial traction, but was ultimately shut down in 2012.}

	\twentyitem
    	{May 2008 –}
	{May 2012}
        {Owner, Scientific Software Architect}
        {John Metta, LLC}
        {}
        {\begin{itemize}
        \item\textbf{2010–2012}: Architect new OASIS modeling application and database system for Hydrologics, Inc for use on NYC water supply. Train Hydrologics team on advanced development.
        \item\textbf{2008-2010}: Subcontractor to Army Corps of Engineers performing scientific data acquisition, analysis, and application development.
        \end{itemize}
        }

	\twentyitem
    	{Jan 2007 –}
	{May 2008}
        {Water Quality Hydrologist}
        {Oregon Department of Environmental Quality}
        {}
        {Mathematical modeling of the Oregon river systems to support \mbox{development} of water quality regulations. Programmed main \mbox{temperature} modeling system (Heatsource).}
        
        \twentyitem
        {Jan 2005 –}
        {Dec 2007}
        {Programmer, Research Assistant}
        {Oregon State University}
        {Biosystems Modeling Group}
        {Provide software development and math/environmental systems modeling for the Biosystems Modeling Group.}
        
        \twentyitem
        {Jun 2003 –}
        {Dec 2004}
        {Programmer, Research Assistant}
        {Oregon State University}
        {Geosciences Department}
        {Develop a graphical user interface and 3-dimensional visualization library to support a large-scale geomorphology model.}
        
        \twentyitem
        {Sep 2000 –}
        {Jun 2003}
        {Undergraduate Research Assistant}
        {College of Charleston}
        {}
        {Various software development (remote sensing, hydrology) and teaching (Python programming, robotics) positions with Geosciences Department, Anthropology Department, US Forest Service, and Charleston County School District. }
        
	%\twentyitem{<dates>}{<Optional under dates>}{<title>}{<company>}{<Optional above description>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem
    	{2003 - 2007}
        {MEng, Msci}
        {Double Masters: Engineering, Geography}
        {\href{http://www.oregonstate.edu/}{Oregon State University, OR}}
        {\textbf{Ecological Engineering:} Environmental systems modeling}
        {\textbf{Physical Geography:} Water resources management}
	\twentyitem
    	{1997 - 2003}
	{}
        {Double Bachelors: Anthropology, Geology}
        {\href{http://www.cofc.edu/}{College of Charleston, SC}}
        {Anthropology Department, Geosciences Department}
        {}
	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 PUBLICATIONS
%----------------------------------------------------------------------------------------
%\section{Publications}
%\begin{itemize}
%\item\textbf{Poor, C., et. al.} (2004) Improvement of Process Description in Conceptual Runoff Models in Un-gauged Basins: A Case Study of Landuse Effects on Water Quality., Eos Trans. AGU, 85(17), Jt. Assem. Suppl., Abstract H53B-04.
%\item\textbf{Currie, M.B. and Pennington, J.W.} (2001) Robots Are Your New Classmates: Using Robotics to Teach Earth Science in Your Classroom., Proceedings: South Carolina Science Council Annual Meeting.
%\end{itemize}

%----------------------------------------------------------------------------------------
%	 MILITARY
%----------------------------------------------------------------------------------------
\section{Military}
\begin{twenty} % Environment for a list with descriptions
	\twentyitemshort
	{1991 - 1996}
	{\textbf{United States Navy} $\textbullet$ Submarine Sailor}
	\twentyitemshort
	{1989 - 1991}
	{\textbf{United States Army} $\textbullet$ Surgeon's Assistant \textit{(Deployed: Desert Storm)}}
\end{twenty}	

\end{document} 
